\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-09-21 manuscript.Rmd

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true, fontsize = 18 ]

@@

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower")
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```

>>>>

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 7, height = 1, fixedsize = true, fontsize = 18 ]

@@

ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
#to show pvalue in the fig add p.mat=p.mat
```
